Incentivizing Exploration with Heterogeneous Utilities

### 2018-01-25 colt.tex
editted the proof in equation (6)

Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
Since
\begin{align}
d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
\end{align}

and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have

\begin{align}
&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber  
\end{align}

Based on our calculation, we know

@@

In this section, we prove

>>>>

Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$. Based on our calculation (see appendix for details), we know

@@

In this section, we prove
\begin{align}
\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]=\frac{z_{t,1}^2}{2}. \nonumber 
\end{align}

Denote $w(x)=\sqrt{x}$. Then $w(x+y)=\sqrt{x} + y\frac{1}{2\sqrt{x}}+O(x^{-3/2})$. Thus, we know

\begin{align}
&\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right] \nonumber \\
=& \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
= & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}+O((z_{t,1}^2+(\sqrt{t}+z_{t,2})^2)^{-3/2})-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
= & \lim_{t\rightarrow\infty} t \times \frac{z_{t,1}^2}{2(z_{t,1}^2+(\sqrt{t}+z_{t,2})^2)} \rightarrow \frac{z_{t,1}^2}{2}. \nonumber 
\end{align}

Therefore, we know Equation~\eqref{ex:limit} holds true.
